A Large-Scale Study of Polymorphism in R

### 2019-04-06 paper/main.tex
small changes, edits, still working on related work

% https://www.r-pkg.org/downloaded
\begin{figure}[!th]{\footnotesize\begin{tabular}{@{}r||l|r|r|r|r|r@{}}\hline
\bf Package & \bf Description & \bf R LOC &\bf C LOC &\bf Scripts & \bf Calls Observed & \bf Calls Recorded \\
\hline
\tt Rcpp  & Seamless C++ integration & 2.2K & 4.2K & 25 & 55K & 340 \\
\tt rlang & Functions for 'Tidyverse' & 7.0K & 6.1K & 122 & 3,924K & 8,422 \\
\tt glue  & Interpreted string literals & 0.3K & 0.3K & 8 & 4K & 145 \\
\tt tibble & Simple data frames & 2.0K & 0.3K & 16 & 1,332K & 6,367 \\
\tt stringi &  String processing & 1.5K & 515K & 64 & 923K & 873 \\
\tt ggplot2 & Data visualisations & 14K & 0 & 130 & 153K & 4,608 \\
\tt dplyr  &  Data manipulation & 4.5K & 4.7K & 78 & 233K & 3,099 \\
\tt pillar & Formatting for columns & 1.4K & 0 & 13 & 803K & 1,514 \\
\tt R6 & Classes w. ref. semantics & 0.7K & 0 & 2 & 1K & 330 \\
\tt stringr & String operations & 0.5K & 0 & 32 & 1,764K & 534 \\
\end{tabular}}\caption{10 Most Downloaded Packages.}\label{most}
\end{figure}

Figure~\ref{most} shows the ten most downloaded CRAN packages.  For each
one, we list how many lines of R and C/C++ the packages contains.  We show
the number of scripts that could be extracted from the package. Each script
corresponds to either one use-case or a set of unit tests. We print the
number of function calls that were observed by our infastructure, and the
number of unique signatures that were recorded.

Our infrastructure only retains unique argument/return combinations. Thus,
while we observe large number of functions being called with different
values, the types of these function call are often similar. Over the entire
corpus, we can see the relation between observed and recorded calls in
Figure~\ref{recorded}.  The median number of observed calls is 82 and
maximum is 19 million.  The median number of recorded signatures is 16 and
the maxium is 8,422. These numbers are skewed by a number of scripts doing
very few calls before plunging into C code.

@@

\newpage
\section{Methods}

@@

More generally, there is an existing literature on analyzing usage patterns of language features.  
For instance, the dynamic features of Smalltalk were analyzed in some work~\cite{callau2011howdevelopers},

@@

%
%.
%
%
%
%
\section{Conclusions and Future Work}

>>>>

% https://www.r-pkg.org/downloaded
\begin{figure}[!th]{\footnotesize\begin{tabular}{@{}r||l|r|r|r|r|r@{}}\hline
\bf Package & \bf Description & \bf R LOC &\bf C LOC &\bf Scripts & \bf Calls Observed & \bf Signatures Recorded \\
\hline
\tt Rcpp  & Seamless C++ integration & 2.2K & 4.2K & 25 & 55K & 340 \\
\tt rlang & Functions for 'Tidyverse' & 7.0K & 6.1K & 122 & 3,924K & 8,422 \\
\tt glue  & Interpreted string literals & 0.3K & 0.3K & 8 & 4K & 145 \\
\tt tibble & Simple data frames & 2.0K & 0.3K & 16 & 1,332K & 6,367 \\
\tt stringi &  String processing & 1.5K & 515K & 64 & 923K & 873 \\
\tt ggplot2 & Data visualisations & 14K & 0 & 130 & 153K & 4,608 \\
\tt dplyr  &  Data manipulation & 4.5K & 4.7K & 78 & 233K & 3,099 \\
\tt pillar & Formatting for columns & 1.4K & 0 & 13 & 803K & 1,514 \\
\tt R6 & Classes w. ref. semantics & 0.7K & 0 & 2 & 1K & 330 \\
\tt stringr & String operations & 0.5K & 0 & 32 & 1,764K & 534 \\
\end{tabular}}\caption{10 Most Downloaded Packages.}\label{most}
\end{figure}

Figure~\ref{most} shows the ten most downloaded CRAN packages.  For each
one, we list how many lines of R and C/C++ the packages contains.  We show
the number of scripts that could be extracted from the package. Each script
corresponds to either one use-case or a set of unit tests. We print the
number of function calls that were observed by our infrastructure, and the
number of unique call signatures that were recorded.

Our infrastructure only retains unique argument/return combinations. Thus,
while we observe large number of functions being called with different
values, the types of these function call are often similar. Over the entire
corpus, we can see the relation between observed and recorded calls in
Figure~\ref{recorded}.  The median number of observed calls is 82 and
maximum is 19 million.  The median number of recorded signatures is 16 and
the maximum is 8,422. These numbers are skewed by a number of scripts doing
very few calls before plunging into C code.

@@

\newpage
\section{Methodology}

@@

More generally, there is an existing literature on analyzing usage patterns of language features.  
For instance, the dynamic features of Smalltalk were analyzed in some work~\cite{callau2011howdevelopers}, which aimed to see how often the highly dynamic capabilities of Smalltalk were used and in which kinds of projects.

@@

%
%.
%
%
%
%
\section{Conclusion}
